%Chapter 5

\chapter*{Bibliographie} % Main chapter title

[Shr et al. 13] Meenakshi Shruti Pal, Sushil Kumar Garg,  International Journal of Advanced Research in Computer Engineering and Technology (IJARCET) Volume 2, Issue 6, June 2013

[Oja et al. 02] T. Ojala, M. Pietikinen, T. Menp, Multiresolution Gray-Scale and Rotation In-
variant Texture Classification with Local Binary Patterns. IEEE Transactions on
Pattern Analysis and Machine Intelligence 24 971 987, 2002.

[Har 79] R. Haralick, Statistical ans structural approaches to texture, Proc. Of IEEE, vol.
67, no. 5, pp. 786-804, May 1979.

[Low 99] David G. Lowe, Object recognition from local scale-invariant features , Proceedings of the International Conference on Computer Vision, vol. 2,‎ 1999, p. 1150–1157.

[Sin et al. 15] Singh, Anshuman Vikram, "Content-Based Image Retrieval using Deep Learning" (2015). Thesis. Rochester Institute of Technology.  Accessed from http://scholarworks.rit.edu/theses/88286/2015

[Ma et al. 99] Wei-Ying Ma, B.S. Manjunath, NeTra: A toolbox for navigating large image databases, Journal
Multimedia Systems - Special issue on video content based retrieval archive Volume 7 Issue 3, May 1999 Pages 184 - 198 

[Car et al. 99] Chad Carson, Megan Thomas, Serge Belongie, Joseph M. Hellerstein and Jitendra Malik, Blobworld: a System for Region-Based Image Indexing and Retrieval (long version) EECS Department,University of California, Berkeley,1999


[Yod 08] Josiah Yoder Content-Based Image Retrieval from large Medical Image Databases, Avinash C. Kak, The Purdue Robot Vision Laboratory, School of Electrical and Computer Engineering at Purdue University. 2008

[Nib et al. 93] W. Niblack, R. Barber, W. Equitz, M. D. Flickner, E. H. Glasman, D. Petkovic, P. Yanker, C. Faloutsos, G. Taubin, QBIC project: querying images by content, using color, texture, and shape, in: W. Niblack (Ed.), Storage and Retrieval for Image and Video Databases, Vol. 1908 of SPIE Proceedings,1993, pp. 173-187

[Fli et al.95] Myron Flickner, Harpreet Sawhney, Wayne Niblack, Jonathan Ashley, Qian Huang, Byron Dom, Monika Gorkani, Jim Hafner, Denis Lee, Dragutin Petkovic, David Steele, Peter Yanker, "Query by Image and Video Content: The QBIC System", Computer, vol.28, no. 9, pp. 23-32, September 1995, doi:10.1109/2.410146

[Lux et al. 08] Mathias Lux, Savvas A. Chatzichristofis. LIRE: Lucene Image Retrieval – An Extensible Java CBIR Library. In proceedings of the 16th ACM International Conference on Multimedia, pp. 1085-1088, Vancouver, Canada, 2008

[Lux et al. 13] Mathias Lux, Oge Marques Visual Information Retrieval using Java and LIRE, Morgan Claypool Publishers, 2013

[Des et al. 08] Thomas Deselaers, Daniel Keysers, Hermann Ney Features for Image Retrieval: An Experimental Comparison. Information Retrieval. 2008. Vol. 11. Issue 2. Springer. pp. 77-107.

[Roe et al. 92] Anna W. Roe,a Sarah L. Pallaqb Young H. Kwon, and Mriganka Sur, Visual projections routed to the auditory pathway in ferrets: receptive fields of visual neurons in primary auditory cortex, The Journal of Neuroscience, September 1992, 12(g): 36513664

[Mit et al. 97] Tom Mitchell, McGraw Hill, Machine Learning Textbook 1997.

[Goo et al. 16] Ian Goodfellow, Yoshua Bengio, Aaron Courville, 2016, Deep Learning, Book in preparation for MIT Press, http://www.deeplearningbook.org

[Mar et al. 89] H. Martens and T. Naes, Multivariate Calibration, John Wiley, Sons Inc., New York, 1989.

[Moo 65] Gordon E. Moore, Cramming More Components Onto Integrated Circuits, Electronics, vol. 38,‎ 19 avril 1965

[Ben 14] Yoshua Bengio. Deep Learning. Machine Learning Summer School, Iceland 2014.

[Hub et al. 68] Hubel, D. and Wiesel, T. (1968). Receptive fields and functional architecture of monkey striate cortex. Journal of Physiology (London), 195, 215–243

[LeCun et al. 98] Y. LeCun, L. Bottou, Y. Bengio, and P. Haffner. "Gradient-based learning applied to document recognition." Proceedings of the IEEE, 86(11):2278-2324, November 1998. 

[Kri et al. 12] Krizhevsky, Sutskever, and Hinton, ImageNet Classification with Deep Convolutional Neural Networks, NIPS 2012.

[CS231n 16] CS231n: Convolutional Neural Networks for Visual Recognition (January - March, 2016),Fe-Fei Li, Andrej Karpathy, Justin Johnson, Stanford University.

[Site1] http://deeplearning4j.org/deepautoencoder.html

[Site2] Li Jiang, Musings on Deep Learning https://medium.com/global-silicon-valley/machine-learning-yesterday-today-tomorrow-3d3023c7b519\#.u0qtths18


[Rus et al.,15] Olga Russakovsky*, Jia Deng*, Hao Su, Jonathan Krause, Sanjeev Satheesh, Sean Ma, Zhiheng Huang, Andrej Karpathy, Aditya Khosla, Michael Bernstein, Alexander C. Berg and Li Fei-Fei. (* = equal contribution) ImageNet Large Scale Visual Recognition Challenge. IJCV, 2015. Volume 115, Issue 3 , pp 211-252 

[Li et Wan.,03] Jia Li, James Z. Wang, ``Automatic linguistic indexing of pictures by a statistical modeling approach,'' IEEE Transactions on Pattern Analysis and Machine Intelligence, vol. 25, no. 9, pp. 1075-1088, 2003.

[Wan et al.,01] James Z. Wang, Jia Li, Gio Wiederhold, SIMPLIcity: Semantics-sensitive Integrated Matching for Picture LIbraries, IEEE Trans. on Pattern Analysis and Machine Intelligence, vol 23, no.9, pp. 947-963, 2001.

[Fei et al. 04] L. Fei-Fei, R. Fergus and P. Perona. Learning generative visual models from few training examples: an incremental Bayesian approach tested on 101 object categories. IEEE. CVPR 2004, Workshop on Generative-Model Based Vision. 2004

[Cha et al.14] K Chatfield, K Simonyan, A Vedaldi, A Zisserman - Return of the devil in the details: Delving deep into convolutional nets, British Machine Vision Conference, 2014.

[LeCun et al. 89] LeCun, Y., Boser, B., Denker, J.S., Henderson, D., Howard, R.E., Hubbard, W., Jackel, L.D.: Backpropagation applied to handwritten zip code recognition. Neural
Comput. 1(4), 541–551 (1989)

[Zei et al. 14] M.D. Zeiler, R. Fergus Visualizing and Understanding Convolutional Networks, ECCV 2014 (Honourable Mention for Best Paper Award)

[Gru et at. 06] M. Grubinger, P. Clough, and H. Muller and T. Deselaers, "The IAPR TC-12 Benchmark: A New Evaluation Resource" for Visual Information Systems,” Proc. of the Intl. Workshop OntoImage’2006 Language Resources for CBIR, 2006.

[Theano 16] Theano Development Team, Theano: A {Python} framework for fast computation of mathematical expressions, arXiv e-prints, 2016.

[Mer et al. 15] Bart van Merriënboer, Dzmitry Bahdanau, Vincent Dumoulin, Dmitriy Serdyuk, David Warde-Farley, Jan Chorowski, and Yoshua Bengio, "Blocks and Fuel: Frameworks for deep learning," arXiv preprint arXiv:1506.00619 [cs.LG], 2015.

[Ale et al. 11] Alex Krizhevsky Geoffrey E. Hinton, Using Very Deep Autoencoders for Content-Based Image Retrieval, Conference: ESANN 2011, 19th European Symposium on Artificial Neural Networks, Bruges.